---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(modelr)
library(broom)
library(ggfortify)
library(infer)
```
#Question 1:
Load the data into a dataframe project

```{r}
project <- data.frame(read_csv("data/project_management.csv"))
project
```

#Question 2:
Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.

```{r}
project %>% 
  ggplot()+
  aes(x = estimated_length, y = actual_length)+
  geom_point()
  
```

#Question 3:
Calculate the correlation coefficient of estimated_length and actual_length and interpret the value you obtain.

```{r}
project %>% 
  summarise(cor(estimated_length, actual_length))
```
The correlation coefficient of estimated_length and actual_length is 0.804 which suggests that these variables are very strongly positively correlated.


#Question 4:
Perform a simple linear regression using -
actual_length  - dependent variable
estimated_length  - independent variable. 

Save the model object to a variable.

```{r}
model <- lm(formula = actual_length ~ estimated_length, data = project)
model
```

1. actual_length is the outcome variable and estimated_length is the single explanatory variable
2. tilde operator (is a function of) which means actual_length varies with estimated_length
3. the modelr package offers functions that allow us to deal with lm() output in a tidy way.

best fit line found by R is 

actual_length =  1.223  +   1.416   * estimated_length

```{r}
project <- project %>% 
  add_predictions(model) %>% 
  add_residuals(model)
project
```

We can then use the predicted outcomes to plot the best fit line

```{r}
project %>% 
  ggplot()+
  aes(x = estimated_length, y = actual_length)+
  geom_point()+
  geom_line(aes(y = pred, col = "red"))
```

#Question 5:
Interpret the regression coefficient of estimated_length (i.e. slope, gradient) you obtain from the model. How do you interpret the r2 value reported by the model?

A 1 unit increase in explanatory variable value changes the outcome variable value by an amount equal to b1

A 1 day increase in the estimated_length of job day(explanatory variable value) changes the predicted day(outcome variable value) by 1.223 

```{r}
summary(model)
```

```{r}
glance_project <- janitor::clean_names(glance(model))
glance_project
```
```{r}
glance_project$r_squared
```
<br>
glance function returns many parameters which suggests that how well the model fits the data.

r-squared is formally known as coefficient of determination
r2  can be interpreted as the proportion of the variation in the outcome variable that can be explained by
variation in the explanatory variable (or explanatory variables for multiple regression).

So, in the case above, our simple linear model says that 64.73% of the variation in actual_length in the sample data can be explained by variation in estimated_weight.

<br>
#Question 6:
Is the relationship statistically significant? Remember, to assess this you need to check the p-value of the regression coefficient (or slope/gradient). But you should first check the regression diagnostic plots to see if the p-value will be reliable (don’t worry about any outlier points you see in the diagnostic plots, we’ll return to them in the extension).

```{r}
autoplot(model)
```

we’re going to bootstrap to extract the slope, i.e. the coefficient of estimated_weight.

```{r}
# specify regression formula
# stat = "slope" extracts the regression coefficient
bootstrap_distribution_slope <- project %>%
  specify(formula = actual_length ~ estimated_length) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "slope")

slope_ci95 <- bootstrap_distribution_slope %>%
  get_ci(level = 0.95, type = "percentile")
slope_ci95
```
```{r}
bootstrap_distribution_slope %>%
  visualise(bins = 30) +
  shade_ci(endpoints = slope_ci95)

```

lower_ci - 0.8763705
upper_ci - 1.615486	

0 is not within the 95% confidence interval, so we can be confident at that level that the coefficient of estimated_length is significantly different from 0.
<br>
Let’s compare this bootstrapped CI with the one we get directly from the lm() output via tidy()

```{r}
janitor::clean_names(tidy(model, conf.int = TRUE, conf.level = 0.95))
```

