---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(prob)
```

1. If I roll a six-sided dice once, what is the probability of getting a number less than 5?
```{r}

rd %>% rolldie(6) %>% 
  filter(X1<5) %>% 
  summarise(prob = n()/nrow(rd))
rd
```

2. How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
rolldie(3) %>% 
  nrow()
```

3. In an experiment where we roll four dice:

how many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)?
what is the probability of this event?
what assumptions do we apply in answering part ii?
```{r}
die_event <- rolldie(4)
```

```{r}
die_event %>% 
  mutate(total = rowSums(die_event)) %>% 
  filter(total %in% c(5,6,7)) %>% 
  summarise(prob = n()/nrow(die_event))

```
4. Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

```{r}
people <- c("h1", "h2","h3", "h4", "h5")

people_order <- 
   permutations(
  n = 5,
  r = 5, 
  v = people,
  repeats.allowed = FALSE
)
dim(people_order)


```

```{r}



people_order <- as_tibble(
   permutations(
  n = 5,
  r = 5, 
  v = people,
  repeats.allowed = FALSE
))


nrow(people_order)
class(people_order)

```


```{r}
people <- c("5", "6","4", "3", "2")
people
```

5. I roll six dice:

what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?
[Hint have a look at the isin() function in the prob package. For example, to filter all rows containing 6, 1, 2 in that order, you could use isin(., c(6, 1, 2), ordered = TRUE)]
```{r}
rolldie(6)

```

