---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
library(janitor)
library(MASS)
```
#1.1 Question 1
##Load the data, clean_names() and explore it.

```{r}
dist <- read_csv("data/20190928-items.csv") %>% 
  clean_names()

dist
```



```{r}
samsung_ratings <- dist %>% 
  filter(brand == "Samsung") %>% 
  arrange(rating)
samsung_ratings
```

#1.2 Question 2
##Find the brand with the highest numbers of phones in the dataset.

```{r}

dist %>% 
  group_by(brand) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(1)

```

#1.3 Question 3
##For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?

###[Hint - you will need to calculate the mean() and sd() of the ratings to plot the appropriate normal. Alternatively, investigate using the fitdistr() function in the MASS package]

```{r}
samsung_stat <- dist %>% 
 filter(brand == "Samsung") %>% 
    summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating))
samsung_stat

```

```{r}

dist %>% 
  filter(brand == "Samsung") %>%
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 25) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = samsung_stat$mean, 
      sd = samsung_stat$sd
    ),
    col = "red"
  )
  
```

# Question 4
##We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.

###Hint
###Further hint - code to filter within one SD

```{r}
samsung_ratings %>%
  filter(rating >= samsung_stat$mean - samsung_stat$sd) %>%
  filter(rating <= samsung_stat$mean + samsung_stat$sd) %>%
  summarise(prop_within_1sd = n() / nrow(samsung_ratings))
```
```{r}
samsung_ratings %>%
  filter(rating >= samsung_stat$mean - (2*samsung_stat$sd)) %>%
  filter(rating <= samsung_stat$mean + (2*samsung_stat$sd)) %>%
  summarise(prop_within_2sd = n() / nrow(samsung_ratings))
```

```{r}
samsung_ratings %>%
  filter(rating >= samsung_stat$mean - (3*samsung_stat$sd)) %>%
  filter(rating <= samsung_stat$mean + (3*samsung_stat$sd)) %>%
  summarise(prop_within_3sd = n() / nrow(samsung_ratings))
```

