---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(fastDummies)
library(ggfortify)
```

#Load the diamonds.csv data set and undertake an initial exploration of the data. You will find a description of the meanings of the variables on the relevant Kaggle page

```{r}
diamonds <- read_csv("data/diamonds.csv")
diamonds
```
<br>
#We expect the carat of the diamonds to be strong correlated with the physical dimensions x, y and z. Use ggpairs() to investigate correlations between these four variables.

```{r}
alias(lm(carat ~ ., data = diamonds))
```
<br>
```{r}
library(GGally)
```
```{r}
ggpairs(diamonds, column =  c("carat", "x", "y", "z"), progress = FALSE)
```

Response variable is carat. Predictors are x, y and z. We see that the correlation is very strong because the correlation coefficient is 0.95.

<br>

#So, we do find significant correlations. Let’s drop columns x, y and z from the dataset, in preparation to use only carat going forward.

```{r}
diamonds_new <- diamonds %>% 
  select(-c("x", "y", "z"))

diamonds_new
```

#We are interested in developing a regression model for the price of a diamond in terms of the possible predictor variables in the dataset.

##Use ggpairs() to investigate correlations between price and the predictors (this may take a while to run, don’t worry, make coffee or something).


```{r}
ggpairs(diamonds_new, progress = FALSE)
```
Carat - predictor variable
Price - response variable

Found a strong positive correlation between carat and price.

##Perform further ggplot visualisations of any significant correlations you find.

```{r}
diamonds_new %>% 
  ggplot(aes(x = carat, y = price))+
  geom_point()
```

#Shortly we may try a regression fit using one or more of the categorical predictors cut, clarity and color, so let’s investigate these predictors:


#Investigate the factor levels of these predictors. How many dummy variables do you expect for each of them?

#Use the dummy_cols() function in the fastDummies package to generate dummies for these predictors and check the number of dummies in each case.

CREATING DUMMY VARIABLES FOR CUT,CLARITY AND COLOR

```{r}
unique(diamonds_new$cut)
```
Fair - 1
Good - 2
Very Good - 3
Premium - 4
Ideal - 5

```{r}
diamonds_new <- diamonds_new %>% 
  mutate(
    cut = case_when(cut == "Fair" ~1,
                    cut == "Good" ~2,
                    cut == "Very Good" ~3,
                    cut == "Premium" ~4,
                    cut == "Ideal" ~5)
  )
diamonds_new
```

```{r}
unique(diamonds_new$clarity)
```
```{r}
diamonds_new1 <- diamonds_new %>% 
  dummy_cols(
    select_columns = "clarity",
    remove_first_dummy = TRUE,
    remove_selected_columns = TRUE
  )

diamonds_new1
```

For clarity, we created 7 dummy variables


```{r}
unique(diamonds_new1$color)
```
```{r}
diamonds_new2 <- diamonds_new1 %>% 
  dummy_cols(
    select_columns = "color",
    remove_first_dummy = TRUE,
    remove_selected_columns = TRUE
  )

diamonds_new2
```

 For color, we created 6 dummy variables
 

#Start with simple linear regression. Regress price on carat and check the regression diagnostics.

lets find model with the above explanatory variable

```{r}
model1 <- lm(price ~ carat, data = diamonds_new2)
model1
```

```{r}
autoplot(model1)
```



```{r}
summary(model1)
```
How much explaining is the model doing?

85% of variation in price is explained by carat(x variable)
For every 1 carat weight increase , the price will increase by 7756 dollars, however all other variables are constant


#Add another predictor of your choice. Check your assumptions, diagnostics, and interpret the model.

Predictor = cut

```{r}
diamonds_new2
```

```{r}
model2 <- lm(price ~ carat + cut, data = diamonds_new2)
model2
```
```{r}
summary(model2)
```
How much explaining is the model doing?

85% of variation in price is explained by cut(x variable)

```{r}
names(diamonds_new2)
```


```{r}
model3 <- lm(price ~ carat + clarity_IF + clarity_SI1 + clarity_SI2 + clarity_VS1 + clarity_VS2 + clarity_VVS1 +  clarity_VVS2, data = diamonds_new2)

model3
```


```{r}
autoplot(model3)
```

```{r}
summary(model3)
```


```{r}
model4 <- lm(price ~ carat + clarity_IF + clarity_SI1 + clarity_SI2 + clarity_VS1 + clarity_VS2 + clarity_VVS1 +  clarity_VVS2+ color_E+ color_F + color_G + color_H + color_I + color_J, data = diamonds_new2)

```

```{r}
summary(model4)
```

It is determined that clarity and colour variables are statistically significant. 