---
title: "R Notebook"
output: html_notebook
---

```{r}
library (tidyverse)
library(GGally)
```


LOADING THE DATASET

```{r}
king_county <- read_csv("data/kc_house_data.csv")

king_county
```

Tidy up the data ready for regression:

* You might like to think about removing some or all of `date`, `id`, `sqft_living15`, `sqft_lot15` and `zipcode` (`lat` and `long` provide a better measure of location in any event).

```{r}
king_county_tidy <- king_county %>% 
  
  select(-c("date", "id", "sqft_living15", "sqft_lot15", "zipcode"))

king_county_tidy

```

Have a think about how to treat `waterfront`. Should we convert its type?

```{r}
unique(king_county_tidy$waterfront)

```

We converted `yr_renovated` into a `renovated` logical variable, indicating whether the property had ever been renovated. You may wish to do the same.

```{r}
king_county_tidy <- king_county_tidy %>% 
  mutate(yr_renovated = ifelse(yr_renovated == 0, TRUE, FALSE))

king_county_tidy
```

Have a think about how to treat `condition` and `grade`? Are they interval or categorical ordinal data types?

```{r}
unique(king_county_tidy$grade)
```

Question 2
Check for aliased variables using the alias() function (this takes in a formula object and a data set). [Hint - formula price ~ . says ‘price varying with all predictors’, this is a suitable input to alias()]. Remove variables that lead to an alias. Check the ‘Elements of multiple regression’ lesson for a dropdown containing further information on finding aliased variables in a dataset.

```{r}
alias(lm(price ~., data = king_county_tidy))
```



```{r}
king_county_numeric <- king_county_tidy %>%
  select_if(is.numeric)

king_county_numeric

king_county__nonnumeric <- king_county_tidy %>%
  select_if(function(x)!is.numeric(x))

king_county__nonnumeric 

king_county_nonnumeric$price <- king_county_tidy$price

ggpairs(king_county_numeric)
ggpairs(king_county_nonnumeric)
```

