---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)
```

#2.1 Question 1
We are going to use a dataset on house sales in Ames, Iowa over a number of years. We will be interested in the SalePrice of houses (though we should clean_names() the data, so this will end up as sale_price). Load the data and explore it.

```{r}
ames <- read_csv("data/ames.csv") %>% 
  janitor::clean_names()
ames 

```
#2.2 Question 2
Plot a histogram of sale_price. Is the distribution normal?

```{r}
options(scipen = 999)
ames %>% 
  ggplot()+
  aes(x = sale_price)+
  geom_histogram(col = "white",bins = 35)
```

#2.3 Question 3
#Calculate the population parameter mean of sale_price. Store it in a variable, as we’ll need this value later when we check if each CI contains the parameter value or not.


```{r}

mean_house_sp <- ames %>% 
  summarise(
    mean_sale_price = mean(sale_price)
  )

mean_house_sp
```
#Now we are going to: - take 1000 random samples each of size 100 from sale_price in ames - create a boostrap sampling distribution of mean(sale_price) from each 100-observation sample (use 1000 reps) - calculate the 95% CI for each bootstrap distribution - store the upper and lower bounds of the CI in a tibble called results

#Use the infer workflow to generate the bootstrap distributions and CIs. This code will be pretty hard to write. Think about wrapping the sample creation and infer code in a for loop to generate 1000 random samples and CIs. Create an empty results tibble before the loop, and bind_rows() to it every time you generate a new set of CI bounds.

#There’s an outline of the code below, and the full solution below that (if you get stuck). Have a go, but don’t spend too long on this, it’s more important to spend your time thinking about CIs!

```{r}

  # get a new 100-observation random sample from ames
  this_sample <- ames %>%
    rep_sample_n(size = 100, replace = FALSE, reps = 1)

  this_sample_mean <- this_sample %>% 
    summarise(
    mean_sample_sale = mean(sale_price)  
  )

ci_95 <- this_sample %>% 
  summarise(
    mean = mean(sale_price),
    lower_bound = quantile(mean, probs = 0.025),
    upper_bound = quantile(mean, probs = 0.975)
  )

ci_95

  # get 95% CI for this_bootstrap distribution
  this_ci <-  this_sample_mean %>%
    get_ci(level = 0.95, type = "percentile")

  this_ci
  
  # prepare new row for results, storing this_ci bounds
  this_result <- c(
    sample_num = sample_num, 
    lower = this_ci %>% 
      pull(lower_ci), 
    upper = this_ci %>%
      pull(upper_ci)
  )
  
  # add this_result to growing tibble of results
  results <- results %>% 
    bind_rows(this_result)
}

results
```

# Question 5
#Pipe results to mutate() to add a new variable popn_param_in_ci which will be TRUE if the population parameter we calculated earlier is between lower and upper, and FALSE otherwise.

#[Hint if you stored your parameter in a tibble earlier (e.g. as the result of a summarise() pipe), extract it here as a numeric before you compare with upper and lower]



```{r}
mean_house_sp <- as.numeric(mean_house_sp)
mean_house_sp

abc <-  results %>% 
  mutate(popn_param_in_ci = mean_house_sp >= lower & mean_house_sp <= upper)
abc

```



```{r}
abc %>% 
  filter(popn_param_in_ci == FALSE)
```

#2.6 Question 6
#Perform an appropriate summarise() to determine the proportion of CIs that contain the population parameter. Our confidence level was 95% (equivalent to a proportion of 0.95). Is your proportion close to that value?

```{r}
abc %>% 
  summarise(
    prop = mean(popn_param_in_ci)
  )
```

#2.7 Question 7
#Have a think about what all this means, make a list of any points you don’t understand. - Imagine you had only a single 100-observation sample of the ames data (say from a 100 house survey). - Would you know ahead of time whether the CI for mean(sale_price) from your particular sample contains the correct population parameter or not?