---
title: "R Notebook"
output: html_notebook
---

```{r}
library(CodeClanData)
library(tidyverse)
library(lubridate)
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
```
#4 MVP
##4.1 Part 1

```{r}
qb_revenue_breakdown

```
###Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
library(wesanderson)
qb_revenue_breakdown %>% 
  janitor::clean_names() %>% 
  ggplot()+
  aes(x = year, y = revenue, fill = product)+
  geom_col(width = 0.5)+
  labs(
    x = "Year\n",
    y = "Revenue",
    title = "Sources of Revenue",
    subtitle = "(2018-2019)\n",
    fill = "Product"
  ) +
  scale_y_continuous(breaks = c(5000,10000,15000,20000,25000,30000))+
  scale_fill_manual(values =col_scheme)+
  theme_minimal()+
  theme(axis.text = element_text(size = 12))
 
  
  
  
```
###Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).



```{r}
qb_monthly_sales %>% 
  janitor::clean_names() %>% 
    filter(cashflow == "Kwikbit Unit 1 Sales" )
```

```{r}
qb_monthly_sales %>% 
  janitor::clean_names() %>% 
    filter(cashflow == "Kwikbit Unit 1 Sales" ) %>% 
  #filter(date >= "2019-01-01" & date <= "2019-12-31") %>% 
  ggplot()+
  aes(x = date, y = amount, colour = cashflow)+
  geom_point(width = 0.5, colour = "blue")+
  geom_line()+
   labs(
    x = "Date\n",
    y = "Amount",
    title = "KwikBit Unit 1 - Sales",
    subtitle = "(2018-2019)\n",
    fill = "Cashflow"
  )+
 # scale_x_discrete(labels = c("Aug18", "Sep18", "Oct18", "Nov18", "Dec18", "Jan19", "Feb19","Mar19","April19", "May19", "June19", "July19"))+
 # scale_fill_manual(values = col_scheme)+
  theme_classic()+
  theme(axis.text = element_text(size = 12))

```

###Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.


```{r}
qb_monthly_sales %>% 
  janitor::clean_names() %>% 
  filter(cashflow %in% c("Total Revenue", "Cost")) %>% 
  group_by(date, cashflow) %>% 
  summarise(monthly_revenue = sum(amount)) %>% 
  ggplot()+
  aes(x = date, y = monthly_revenue, colour = cashflow)+
  geom_line()+
  labs(
    x = "Date\n",
    y = "Monthly Revenue",
    fill = "Cashflow"
  )+
 # scale_x_discrete(labels = c("Aug18", "Sep18", "Oct18", "Nov18", "Dec18", "Jan19", "Feb19","Mar19","April19", "May19", "June19", "July19"))+
 # scale_fill_manual(values = col_scheme)+
  theme_classic()+
  theme(axis.text = element_text(size = 12))


```

###Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.
```{r}
qb_competitors
```
```{r}

qb_competitors %>% 
  janitor::clean_names() %>% 
  ggplot()+
  aes(x = year, y = revenue, fill = company)+
  geom_area()+
  facet_wrap(~company)


  
```

###Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}
qb_competitors %>% 
  janitor::clean_names() %>% 
  group_by(company,year) %>% 
  summarise(revenue_sum = sum(revenue)) %>% 
  ggplot()+
  aes(x = year, y = revenue_sum, colour = company )+
  geom_line(stat = "identity")+
  geom_point()
```
###Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.

```{r}
qb_device_data
names(qb_device_data)
ncol(qb_device_data)
```

```{r}
qb_device_data %>% 
 group_by(device, id) %>% 
 summarise(steps = sum(counts)) %>% 
ggplot()+
 aes(x = device, y = steps)+
 geom_bar(stat = "identity")+
facet_wrap(~device ~id)

```

```{r}
qb_device_data %>% 
  unite("time", hours:mins, sep = ".") %>% 
  ggplot() +
  aes(x = time ,y = counts)+
    geom_line()
```



```{r}
qb_device_data %>% 
  mutate(time = (hours* 60) + mins) %>% 
  ggplot ()+
  aes(x = time, y = counts)+
  geom_line()+
  facet_grid(~device ~id)
```

```{r}

```


```{r}

```

