--- title: "R Notebook" 
output: html_notebook ---

#loading library
```{r} 
library(tidyverse) 

``` 

#reading dataset 
```{r} 
movies_hw <-
read_csv("data/movies.csv")
movies_hw 
``` 

```{r} 
names(movies_hw) 
```

```{r} 
str(movies_hw) 
```

#Answer 1

#have read the data #assigned it to the variable movies_hw 
#original_title and title are almost same except one. Therefore we can have just one column saying film_title. 
#revenue column has zero in few places. May  be the data is
#unavailable/NA in that case

#Answer 2

#selecting three columns using pipe 

```{r}
movies_selected <- movies_hw %>%
select(title,runtime,budget) 
movies_selected 
``` 

#Answer 3
#count number of missing values in each column 

```{r}
movies_hw %>%
  summarise(count = sum(is.na(original_title), 
                        is.na(title), 
                        is.na(homepage), 
                        is.na(budget),
                        is.na(original_language), 
                        is.na(overview), 
                        is.na(popularity),
                        is.na(release_date), 
                        is.na(revenue), 
                        is.na(runtime), 
                        is.na(tagline),
                        is.na(vote_average), 
                        is.na(vote_count))) 
```

#Answer 4
#replace 0 with NA for runtime column

```{r}
movies_runtime <- movies_hw %>% 
  mutate(runtime = na_if(runtime,"0"))
movies_runtime

```
```{r}
movies_runtime %>% 
  summarise(count = sum(is.na(runtime))) 
```


#Answer 5

#replace median runtime using coalesce for runtime column

```{r}
movies_imputed <- movies_runtime%>% 
  mutate (runtime = coalesce(runtime,median(runtime, na.rm = TRUE))) 
movies_imputed

``` 

#counting NAs
```{r} 
movies_imputed %>% summarise (count = sum(is.na(runtime))) 

```

#Answer 6

#slice_min for 10 shortest runtime
```{r} 
movies_imputed %>% slice_min(runtime,n = 10)

```

#slice_max for 10 shortest runtime

```{r} 
movies_imputed %>% slice_max(runtime, n=10)
```

#Answer 7

```{r}
movies_imputed %>% 
  mutate (budget = if_else(budget<100000000,median(budget), budget, missing = NULL) )
movies_imputed
```

