---
title: "R Notebook"
output: html_notebook
---


Clustering homework

You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings.

We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers.

Perform k-means clustering and chose a value of k.

Visualise the clustering for your chosen value of k.

Do you think the clustering seems a good fit for this data?

Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the ‘Segmentation & clustering intro’ lesson).

```{r}
library(janitor)
library(fastDummies)
library(broom)
library(tidyverse)
library(factoextra)
```

```{r}
customers <- read_csv("data/mall_customers.csv") %>% 
  clean_names()
customers
```
```{r}
customers1 <- customers %>% 
  select(annual_income_k, spending_score_1_100) %>% 
  mutate_all(scale)

customers1
  
```


```{r}
clustered_cust <- kmeans(customers1, 2, nstart = 25)

clustered_cust
```



```{r}

fviz_nbclust(customers1, 
             kmeans, 
             method = "wss", 
             nstart = 25)
```

k = 3

Silhouette coefficient

```{r}
fviz_nbclust(customers1, kmeans, method = "silhouette", nstart = 25)
```

k = 3


Gap statistic

```{r}
fviz_nbclust(customers1, kmeans, method = "gap_stat") #would put nstart=25 if had more computing power
```

```{r}
clustered_customers1 <- kmeans(customers1, 5, nstart = 25)

clustered_customers1
```

```{r}
clusters <- augment(clustered_customers1, customers1)

ggplot(clusters, aes(spending_score_1_100, annual_income_k, colour = .cluster)) +
  geom_point() 
```

